\thetitle

### 2009-02-19 paper/paper-unlabelled.tex
labelling equations
darcs-hash:20090219142844-d98fc-bae29ff836240fda827e321c94d273c24149f733.gz

Nondeterminism can now be emulated by instantiating these definitions with a suitable monad and |pick| operation. A deterministic, non-instrumented version can still be obtained, simply by using the identity monad and any deterministic |pick| operation, such as |head| or 'median-of-three'.

>>>>

Nondeterminism can now be emulated by instantiating these definitions with a suitable monad and |pick| operation. A deterministic, non-instrumented version can still be obtained, simply by using the identity monad and any deterministic |pick| operation, such as |head| or 'median-of-three' (not considered here).
